Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-24 thesis.Rmd
la till lite skiss för diskussionen

The results showed significant lower risk for

>>>>

The most common type of OFI is clinical judgement error, it is the most common in all BE shock classes and 2/4 classes for SBP classes. is around ...% of. It generally takes up ...% of all OFI defined as shock (class 2 and below).

When OFI and shock severity are analysed alone, there are statistical significant correlation for these classes: ... . It shows positive correlation where the more severe the shock is, the higher the odds are for an OFI to occur. This in constrast with the adjusted results which showed inverted correlation betwen OFI and shock severity, with 63% lower odds for OFI when comparing the BE class 4 with class 1. However there is no correlation for the other classes nor the classes for the SBP group.

When analysing the other adjusted factors, ISS seems to be a major confounder which correlates to both OFI and shock severity. This can explain why the results of the adjusted and unadjusted analyses are inverted.
